---
title: "EDS212Class2Comp2"
---

## Directions for Git

first type usethis::use_git()

then answer yes twice

now we can make changes and then make sure to save those changes

we now have a local git repo (we will never look at a local one, look at it through github after these next steps)

usethis::use_github()

mine says master instead of main?? is that a problem?? (in the Pushing to Github)

```{r}
library(tidyverse)
library(palmerpenguins)

```

## Plotting Functions in ggplot2

```{r}
fx = function(x) {3 * x^2 + 4}

ggplot(data.frame(x = c(1,100)), aes(x = x)) +
  geom_function(fun = fx)
```

## Partial Derivative

```{r}
#use the expression function to then take a derivative of it
#use function function to just make a function
fxyz = expression(2 * x * y + 3* (x^2) * (z^3))
dfdy = D(fxyz, 'y') #this is a partial derivative
dfdy
```

## Penguin plot

```{r}
#geom_point() for scatterplot
#body_mass for x and flipper length y

ggplot(data = penguins, aes(x=body_mass_g,y=flipper_length_mm, color = species)) +
  geom_point() +
  labs(x = "Body Mass (g)",
       y = "Flipper Length (mm)",
       title = "Palmer Penguins body dimensions") +
  theme_linedraw()
#aes is reserved for mapping variables for chart asthetics
#to change all points to purple, do outside of aes [but still inside ggplot ()]
#to change color of point based on species than do that inside aes!
```
